---
title: "NPX - RIVET: Cleaning and Analysis"
author: "Your Name"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## File Description

This file was created by Alex Haffner in September 2021, updated by Elaine Maskus in October 2021, and updated again by Oskar in November 2022. It prepares data from Rivet School for audit reporting as part of the NPX project.

Input: 

 - 'raw' data file: as received from client and stored in Secure dropbox folder 
 
Ouput: 

 - 'clean' data file for use in reporting and saved in data folder of root project directory 
 
 - tables of impact metrics and exclusion criteria 


```{r packages, message = FALSE, warning=FALSE}

library(tidyverse) 
library(openxlsx) 
library(janitor) 
library(summarytools) 
library(readxl)
library(dplyr)

```

## Loading Data

```{r data, echo=TRUE, eval = TRUE}
# excel data
# df_rivet <- read_xlsx("../Secure/Rivet_Y1_ImpactAudit_211101.xlsx", sheet=1, na = "--") %>%
  # clean_names()

# we received a second version of the data from Alex
# csv data
df_rivet_raw <- read_csv("../Secure/Rivet Yr 2 official audit/NPX Fellows Tracker - Sheet6 Alex.csv", na = c("","N/A","")) %>%
  clean_names() |>
  mutate(enrollment_date = lubridate::mdy(enrollment_date))
```

## check for cases from previous audit 

```{r}
rivet_yr1_df = read.csv("Rivet_Y1_ImpactAudit_Dec2021_Clean.csv") 
# confirm this individual was reported in previous year before filtering 
df_rivet_dedup = df_rivet_raw |> 
  filter(last_name != rivet_yr1_df$last_name & first_name != rivet_yr1_df$first_name)
# check filtering removed the right cases 
# dim(df_rivet_raw)
# dim(df_rivet_dedup)
# for table down below 
reported_out = df_rivet_raw |> 
  filter(last_name == rivet_yr1_df$last_name & first_name == rivet_yr1_df$first_name) |>
  nrow()
```


```{r data, echo=TRUE, eval = TRUE}
# delete empty rows
#df_rivet <- df_rivet %>% 
#  filter(!is.na(first_name))
#68 cases

# remove identifying columns: 

df_rivet = df_rivet_dedup |>
  select(-first_name, -last_name, -email_address, -dob) |>
  mutate(id = seq(1,nrow(df_rivet_dedup))) |>
  relocate(id, everything())
```

## Data Frame Summary and Data Quality Check

Run dfSummary and look at output - look for any outliers or non-standard values

```{r}

view(dfSummary(df_rivet))

```

Check for duplicates

```{r}
df_rivet |> janitor::get_dupes()
# no dupes 
```

clean county of residence
```{r}

table(df_rivet$county_of_residence)

df_rivet <- df_rivet %>% 
  mutate(county_of_residence = case_when(
    county_of_residence == 'Alameda' ~ 'Alameda County',
   # county_of_residence == 'San juaquin' ~ 'San Joaquin County',
    county_of_residence == 'San Francisco' ~ 'San Francisco County',
    county_of_residence == 'Santa Clara' ~ 'Santa Clara County',
    T ~ county_of_residence
  ))


table(df_rivet$county_of_residence)

```


## Filter Data File

This step filters the file to include only records of interest.
- enrolled after Jan 2021
- working towards a Bachelors
- in county of interest
- graduated 

```{r, echo = T}

# creating filter for counties of interest
filter_counties <- c("Alameda County", 
                     "Contra Costa County", 
                     "Marin County", 
                     "Napa County",
                     "Sacramento County", 
                     "San Francisco County", 
                     "San Joaquin County", 
                     "San Mateo County", 
                     "Santa Clara County", 
                     "Santa Cruz County", 
                     "Solano County", 
                     "Sonoma County",
                     "Stanislaus County")

#with graduate filter
df_rivet_fg <- df_rivet %>%
      filter(enrollment_date > "01/01/2021",
             degree_type == "BA",
             county_of_residence %in% filter_counties,
             enrollment_status == "5 BA Grad")

# select only counties of interest
# freq(df_rivet_fg$county_of_residence)


```

## Create df with info on removed / filtered out cases

```{r}

# find those enrolled outside of defined period: 
# from January 1, 2021  to October 31, 2025
 
e_out = df_rivet |>
  filter(enrollment_date <= as.Date("2021-01-01") | enrollment_date >= as.Date("2025-10-31")) |>
  select(id) |> n_distinct()

# e <- 0 #assign count to 0 since none fall out of range

#working towards aa not ba
table(df_rivet$degree_type)
# 
# freak <- freq(df_rivet$degree_type) #creates df of frequency table
# aa <- freak[1,1] 

aa_out = df_rivet |>
  filter(degree_type == "AA") |>
 nrow()

#not in correct county of residence - for july  22 audit, 1 person in Merced County
# freq(df_rivet$county_of_residence)

c_out = df_rivet |>
  filter(!county_of_residence %in% filter_counties) |>
  nrow()

#not yet graduated - only counting active and paused
active_out =
  df_rivet %>% 
  filter(degree_type == "BA",
         enrollment_status %in% c("1 Active")) %>% 
  nrow()
  
paused_out = 
df_rivet %>% 
  filter(degree_type == "BA",
         enrollment_status %in% c("3 Paused A", "3 Paused B")) %>% 
  nrow()

withdrawn_out = 
df_rivet %>% 
  filter(degree_type == "BA",
         enrollment_status %in% c("4 Withdrawn")) %>% 
  nrow()  

total_out <- sum(e_out,aa_out,c_out,active_out, paused_out, withdrawn_out) #total number removed

# create df with above values
way <- c("Student enrolled before January 1, 2021 or after October 31, 2025", 
         "Student lives outside of the Greater Bay Area region", 
         "Student is not currently pursuing a bachelor's degree", 
         'Student is active but has not yet graduated', 
         "Student has paused progress and not yet graduated", 
         'Student has withdrawn from program', 
         'Total Excluded')
#count <- c(e,c,aa,g,wd,t)

excluded <- as.data.frame(way) |>
  mutate(`Number Excluded` = c(e_out, c_out, aa_out, active_out, paused_out, withdrawn_out, total_out)) |> rename('Reason for Exclusion' = way)

```

```{r}
# code each case by exclusion criteria (create binaries for if each case is excluded or not based on each exclusion criteria):
df_rivet = df_rivet |>
  mutate(
    e_out = if_else((enrollment_date <= as.Date("2021-01-01") | enrollment_date >= as.Date("2025-10-31")), 1, 0), # enrollment out of date range 
    aa_out = if_else(degree_type == "AA", 1, 0), # wrong degree type
    c_out = if_else(!county_of_residence %in% filter_counties, 1, 0), # county out of region 
    active_out = if_else(degree_type == "BA"     & enrollment_status %in% c("1 Active"), 1, 0), # not graduated, active
    paused_out = if_else(degree_type == "BA"     & enrollment_status %in% c("3 Paused A", "3 Paused B"), 1, 0), # not graduated, paused
    withdrawn_out = if_else(degree_type == "BA"  & enrollment_status %in% c("4 Withdrawn"), 1, 0) # not graduated, withdrawn
    )

e_out_df = df_rivet |>
  filter(e_out == 1)

c_out_df = df_rivet |>
  filter(!id %in% c(e_out_df$id), #ids from previous step to avoid double counting
         c_out == 1) # condition

aa_out_df = df_rivet |> 
  filter(!id %in% c(e_out_df$id, c_out_df$id), #ids from previous step to avoid double counting
         aa_out == 1) # condition for filter 

active_out_df = df_rivet |>
  filter(!id %in% c(e_out_df$id, aa_out_df$id, c_out_df$id), #ids from previous step to avoid double counting
         active_out == 1)  # condition for filter

pause_out_df = df_rivet |>
  filter(!id %in% c(e_out_df$id, aa_out_df$id, c_out_df$id, active_out_df$id), #ids from previous step to avoid double counting
         paused_out == 1) # condition for filter

withdrawn_out_df = df_rivet |>
  filter(!id %in% c(e_out_df$id, aa_out_df$id, c_out_df$id, 
            active_out_df$id, pause_out_df$id),
         withdrawn_out == 1)

ex_out_vec = c(nrow(e_out_df), 
               nrow(c_out_df), 
               nrow(aa_out_df), 
               nrow(active_out_df), 
               nrow(pause_out_df), 
               nrow(withdrawn_out_df))

excluded2 = as.data.frame(way) |>
  mutate(`Number Excluded` = c(ex_out_vec,
                                sum(ex_out_vec))) |> 
           rename('Reason for Exclusion' = way)

# excluded2 is better bc it avoids double counting,
# but note that order that they are calculated will affect the totals 
# how many individuals excluded for more than 1 reason?
multiple_exclusions = df_rivet |>
  mutate(condition_sum = rowSums(across(e_out:withdrawn_out))) |>
  filter(condition_sum >= 2)
nrow(multiple_exclusions)
```

## make cumulative reporting table



```{r}
# cumulative reporting table

# year 1 impact count: 
ngrad_yr1 = rivet_yr1_df |> nrow()

#  year 2 impact count: 
ngrad_yr2 = df_rivet_fg |> nrow()
  
# cumulative 
ngrad_total = ngrad_yr1 + ngrad_yr2

# make cumulative table for report 
cumulative = tibble(
  `Reporting Year` = 
    # c("Year 1: January 1, 2021 – June 30, 2021",
    #   "Year 2: July 1, 2021 – June 30, 2022",
    #   "**Total**"),
      c("Year 1",
      "Year 2",
      "**Total**"),
  `Number of Graduates` = 
    c(ngrad_yr1, ngrad_yr2, ngrad_total)
)


# create workbook ----
cumulative_out =  createWorkbook()

# add worksheet ----
addWorksheet(cumulative_out, sheetName = "RIVET_cumulative")
# add data 
writeDataTable(cumulative_out, sheet = "RIVET_cumulative", x = cumulative, tableStyle = "none")
# save workbook ----
saveWorkbook(cumulative_out, "data/NPX_RIVET_cumulative_yr2_audit.xlsx", overwrite = TRUE)

```


## Save df's for reporting

**BEFORE SAVING** make sure total number of cases removed + number of cases in df_rivet_fg = total number of cases in file

```{r}
# this asks if:
# (exclusions) + 
# (individuals in the impact metric) + 
# (individuals removed bc they were in last years data) = 
# (number of cases in the raw data set)

(sum(ex_out_vec) + nrow(df_rivet_fg)+ reported_out) == nrow(df_rivet_raw)
# if returns FALSE, stop and figure out why these numbers aren't the same

```


```{r, echo = T}
#data file 
write_csv(df_rivet_fg, "data/RIVET_y2_impact_audit_nov2022_clean.csv") #update date

#removal reason file
write_csv(excluded2,"data/RIVET_y2_impact_audit_nov2022_excluded.csv") #update date

```

