---
title: "NPX - RIVET: Cleaning and Analysis"
author: "Your Name"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## File Description

This file was created by Alex Haffner 9/14/21, updated by Elaine Maskus October 2021, and updated again by Oskar in November 2022. It prepares data from Rivet School for audit reporting as part of the NPX project.

Input: 

 - 'raw' data file: as received from client and stored in Secure dropbox folder 
 
Ouput: 

 - 'clean' data file for use in reporting and saved in data folder of root project directory 
 



```{r packages, message = FALSE, warning=FALSE}

library(tidyverse) 
library(openxlsx) 
library(janitor) 
library(summarytools) 
library(readxl)
library(dplyr)

```

## Loading Data

```{r data, echo=TRUE, eval = TRUE}

# excel data
# df_rivet <- read_xlsx("../Secure/Rivet_Y1_ImpactAudit_211101.xlsx", sheet=1, na = "--") %>%
  # clean_names()

# csv data
df_rivet_raw <- read_csv("../Secure/Rivet Yr 2 official audit/NPX Fellows Tracker - Sheet6 Alex Fernandez.csv", na = c("","N/A","")) %>%
  clean_names()

# delete empty rows
#df_rivet <- df_rivet %>% 
#  filter(!is.na(first_name))
#68 cases

# remove identifying columns: 
set.seed(21)
df_rivet = df_rivet_raw |>
  select(-first_name, -last_name, -email_address, -dob) |>
  mutate(id = seq(1,length(df_rivet[1]))) |>
  relocate(id, everything())

```

## Data Frame Summary and Data Quality Check

Run dfSummary and look at output - look for any outliers or non-standard values

```{r}

view(dfSummary(df_rivet))

```

Check for duplicates

```{r}
df_rivet |> janitor::get_dupes()
# no dupes 
```

clean county of residence
```{r}

table(df_rivet$county_of_residence)

df_rivet <- df_rivet %>% 
  mutate(county_of_residence = case_when(
    county_of_residence == 'Alameda' ~ 'Alameda County',
   # county_of_residence == 'San juaquin' ~ 'San Joaquin County',
   # county_of_residence == 'San Francisco' ~ 'San Francisco County',
    county_of_residence == 'Santa Clara' ~ 'Santa Clara County',
    T ~ county_of_residence
  ))


table(df_rivet$county_of_residence)

```


## Filter Data File

This step filters the file to include only records of interest.
- enrolled after Jan 2021
- working towards a Bachelors
- in county of interest
- graduated 

```{r, echo = T}

# creating filter for counties of interest
filter_counties <- c("Alameda County", 
                     "Contra Costa County", 
                     "Marin County", 
                     "Napa County",
                     "Sacramento County", 
                     "San Francisco County", 
                     "San Joaquin County", 
                     "San Mateo County", 
                     "Santa Clara County", 
                     "Santa Cruz County", 
                     "Solano County", 
                     "Sonoma County",
                     "Stanislaus County")

#with graduate filter
df_rivet_fg <- df_rivet %>%
      filter(enrollment_date > "01/01/2021",
             degree_type == "BA",
             county_of_residence %in% filter_counties,
             enrollment_status == "5 BA Grad")

# select only counties of interest
# freq(df_rivet_fg$county_of_residence)


```

## Create df with info on removed / filtered out cases

```{r}

#enrolled after 1/1/21 - for july  22 audit, no one
#freq(df_rivet$enrollment_date)

e

e <- 0 #assign count to 0 since none fall out of range

#working towards aa not ba
freq(df_rivet$degree_type)

freak <- freq(df_rivet$degree_type) #creates df of frequency table
aa <- freak[1,1] 

#not in correct county of residence - for july  22 audit, 1 person in Merced County
freq(df_rivet$county_of_residence)

c <- 1 #assign count since data are messy

#not yet graduated - only counting active and paused
freak <-
  df_rivet %>% 
  filter(degree_type == "BA") %>% 
  freq(enrollment_status)

wd <- freak[3,1]  #count of withdrawn students
a <- freak[1,1] #count of active students
p <- freak[2,1] #count of paused students

g <- sum(a,p) #combine active and paused students


t <- sum(e,c,aa,g) #total number removed

# create df with above values
way <- c("Student enrolled before January, 1 2021", 'Student lives outside of the Greater Bay Area region', "Student is not currently pursuing a bachelor's degree", 'Student has not yet graduated', 'Student has withdrawn from program', 'Total Removed')
count <- c(e,c,aa,g,wd,t)

removed <- as.data.frame(way)
removed$Count <- count
removed <- rename(removed, 'Reason for Removal' = way,
                  'Number Removed' = Count)

```

## Save df's for reporting

**BEFORE SAVING** make sure total number of cases removed + number of cases in df_rivet_fg = total number of cases in file

```{r, echo = T}
#data file 
write_csv(df_rivet_fg, "Rivet_Y1_ImpactAudit_Dec2021_Clean.csv") #update date

#removal reason file
write_csv(removed,"Rivet_Y1_ImpactAudit_Dec2021_Removed.csv") #update date

```

